\textbf{Response Letter}

### 2018-12-22 doc/aij18/major-revision/evaluation.tex
Further revisions on sections 5 and 6

\begin{enumerate}
	\item The GTM is unknown. This is the most common scenario in ML, where models are both learned and evaluated with respect to datasets.
	\item The GTM is known but a test-based evaluation on a dataset is preferable (or needed as complementary to a syntactic evaluation). As a rule of thumb, it is preferable to evaluate the learned models wrt a dataset because a learned model can be semantically correct though syntactically incorrect (different from the GTM). We refer to this phenomenon as \emph{model reformulation}.
\end{enumerate}

>>>>

\begin{enumerate}
	\item The GTM is unknown. This is the most common scenario in ML, where models are both learned and evaluated with respect to datasets.
%	\item The GTM is known but a test-based evaluation on a dataset is preferable (or needed as complementary to a syntactic evaluation). As a rule of thumb, it is preferable to evaluate the learned models wrt a dataset because a learned model can be semantically correct though syntactically incorrect (different from the GTM). We refer to this phenomenon as \emph{model reformulation}.
	\item \textcolor{red}{We are interested in measuring the ability of a model to explain a given plan trace, which is a good indicator of how the model will perform in actual planning tasks.} As a rule of thumb, it is preferable to evaluate the learned models wrt a dataset because a learned model can be semantically correct though syntactically incorrect (different from the GTM). We refer to this phenomenon as \emph{model reformulation}.
\end{enumerate}

### 2018-12-22 doc/aij18/major-revision/experiments.tex
Further revisions on sections 5 and 6

Our last experiment is devoted to compare the scores provided by the syntactic and semantic versions of precision and recall. For that purpose, we will evaluate the models learned in Section \ref{minimal} both syntactically, using the GTM, and semantically, computing the set of action models closest to the learned models that is compliant with a testing set of five traces (see Definition \ref{compliant}). We must note that since we are using {\sc Madagascar}, a satisficing planner, the solution to the model evaluation may not be the closest compliant model, so the scores of sem-Precision and sem-Recall are approximate values. Our goal with this experiment is to gauge the suitability of the semantic metrics proposed in section \ref{sec:evaluation} with respect to their well-known counterparts. With that in mind, we define two case studies:

>>>>

Our last experiment is devoted to compare the scores provided by the syntactic and semantic versions of precision and recall. For that purpose, we will evaluate the models learned in Section \ref{minimal} both syntactically, using the GTM, and semantically, computing the set of action models closest to the learned models that is compliant with a testing set of five traces (see Definition \ref{compliant}). We must note that since we are using {\sc Madagascar}, a satisficing planner, the solution to the model evaluation may not be the closest compliant domain model, so the scores of sem-Precision and sem-Recall are approximate values. Our goal with this experiment is to gauge the suitability of the semantic metrics proposed in section \ref{sec:evaluation} with respect to their well-known counterparts. With that in mind, we define two case studies:

### 2018-12-22 doc/aij18/major-revision/letter.tex
Further revisions on sections 5 and 6

-          At the bottom of the page, you write that VAL cannot address the model validation of a partial model and on the other hand it requires a full plan and full action model. I don't see how this is "on the other hand"? it is the same "hand"

-          When introducing the semantic evaluation metrics, you provide two justification. One is that there is no GTM. The other is that a test-based evaluation is preferable. The latter justification is not really a justification. It is like saying "we justify using a test-based evaluation by the fact that test-based evaluation is sometimes preferred".

-          What does it mean that a learned action model is sound and complete?

@@

-          "… generated 10 plan traces (each with 10 actions …" – the parenthesis should be removed.

>>>>

-          At the bottom of the page, you write that VAL cannot address the model validation of a partial model and on the other hand it requires a full plan and full action model. I don't see how this is "on the other hand"? it is the same "hand"
\end{mdframed}

-          When introducing the semantic evaluation metrics, you provide two justification. One is that there is no GTM. The other is that a test-based evaluation is preferable. The latter justification is not really a justification. It is like saying "we justify using a test-based evaluation by the fact that test-based evaluation is sometimes preferred".
\end{mdframed}

\textcolor{blue}{We have provided better justification for the use of semantic evaluation metrics.}

-          What does it mean that a learned action model is sound and complete?
\end{mdframed}

\textcolor{blue}{The precision and recall metrics give a notion of the soundness and completeness of a model. By a sound model we understand one where all preconditions and effects are correct, either wrt to the GTM or a test set, so there is no need to remove anything. A complete model is one where no precondition or effect is missing.}

@@

-          "… generated 10 plan traces (each with 10 actions …" – the parenthesis should be removed.
\end{mdframed}
